I am incredibly grateful for the support and mentorship that I have received during my time at Stanford.  

First, my sincere thanks to Professor Fan for his mentorship and guidance throughout my PhD.  From the initial joining of his group through my final projects, he has consistently made himself available and has offered tremendously wise advice for both my technical and professional development.  He has taught me very valuable lessons about being a productive and creative scientist, but also serves as a personal role model for his overwhelming competence and humility.  Additionally, I appreciate the intellectual freedom I was given in exploring a wide range of topics throughout my degree, which was a key ingredient in my motivation to produce meaningful work.

I would also like to thank the members of the ACHIP collaboration, especially Professor Byer, Professor Solgaard, and Dr. England for their guidance and support.  I am forever grateful to have the opportunity to contribute to such an inspiring technology that may one day benefit humanity in a significant way.  The environment in ACHIP has always been supportive, positive, and encouraging of new ideas, which I've appreciated fully.

Much of the work in this thesis is heavily inspired by my interactions and brainstormings with several colleagues.  For the dielectric laser accelerator project, I am especially grateful to Dr. Si Tan for working with me to imagine a integrated photonic circuit for powering the accelerator.  
Also, Zhexin Zhao and Neil Sapra have been highly influential to my work on this project.  In the machine learning-related research, I owe much to Dr. Momchil Minkov and Dr. Ian Williamson for their continued guidance and help in developing the ideas described in this thesis.  Additionally, Ben Bartlett and Sunil Pai have been welcome brainstorming companions.

Finally, I would like to thank my family and close friends for their support and love throughout this process.  Because of their sacrifices, I have been able to enjoy the opportunity to study at Stanford and pursue a scientific training, for which I am eternally grateful.  Furthermore, their company has been of great help during periods of stress and doubt.
